Article data analysis

### 2018-11-01 notebooks/article_notebook.Rmd
updated gene query

```{r ARIBA analysis, include = FALSE}
megares_report_loc <- "../data/ariba/megares_results"
resfinder_report_loc <- "../data/ariba/resfinder_results"
ac_genes <- c("qnr","oqx","qep")
mut_genes <- c("gyr","par","marR","soxR","acrR","mcb")

>>>>

```{r ARIBA analysis, include = FALSE}
megares_report_loc <- "../data/ariba/megares_results"
resfinder_report_loc <- "../data/ariba/resfinder_results"
ac_genes <- c("qnr","oqx","qep","mfp","mcb")
mut_genes <- c("gyr","par","marR","soxR","acrR","nor","ydh","mdf")
